---
title: "Tidyverse Review"
author: "Jack Sylvia"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sectopn 5.1: Billboard

## Aside: Baseline of Zero?

```{r}
library(palmerpenguins)
library(tidyverse)
library(ggplot2)
ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  xlim(c(0,60)) +
  ylim(c(0,25))
```


```{r}
library(tidyverse)
library(billboard)
  head(wiki_hot_100s)
#>   no                     title              artist year
#> 1  1 Theme from A Summer Place         Percy Faith 1960
#> 2  2          He'll Have to Go          Jim Reeves 1960
#> 3  3             Cathy's Clown The Everly Brothers 1960
#> 4  4              Running Bear      Johnny Preston 1960
#> 5  5                Teen Angel        Mark Dinning 1960
#> 6  6                 I'm Sorry          Brenda Lee 1960
tail(wiki_hot_100s)
#>       no                   title
#> 5696  95 Adventure of a Lifetime
#> 5697  96         Humble and Kind
#> 5698  97                  Wicked
#> 5699  98           Tiimmy Turner
#> 5700  99           See You Again
#> 5701 100                 Perfect
#>                                  artist year
#> 5696                           Coldplay 2016
#> 5697                         Tim McGraw 2016
#> 5698                             Future 2016
#> 5699                          Desiigner 2016
#> 5700 Wiz Khalifa featuring Charlie Puth 2016
#> 5701                      One Direction 2016
```


```{r}
wiki_top15 <- wiki_hot_100s %>% 
  as_tibble() %>% 
  filter(year <= 2009 & year >= 2000) %>%
  group_by(artist) %>%
  summarise(nsongs = n()) %>%
  arrange(desc(nsongs)) %>%
  slice(1:15) %>%
  mutate(artist = fct_reorder(artist, nsongs))

ggplot(data = wiki_top15, aes(x = artist, y = nsongs)) +
  geom_col() + coord_flip()
```

## Exercise 2

There is a problem for counting features. Any artist who has a song featuring a different artist will not have that song added to their overall total.

## Exercise 3

```{r}
wiki_hot_100s %>% as_tibble() %>%
  mutate(artist2 = str_remove(artist, 
                              pattern = " featuring .*")) %>%
  tail() %>%
  print(width = Inf)

```


Saving for later....

## Exercise 4/5

```{r}
ggplot(data = wiki_top15, aes(x = artist, y = nsongs)) +
  geom_point(size=3, color = "green", shape=18) + 
  coord_flip() + 
  geom_segment(aes(x=artist, xend=artist, y=0, yend=nsongs-0.25), linetype="dotdash", colour="red") 
```

Using lollipop charts you can add much more artists to the chart while still have the visualization be legible. Having to many bars would be tougher to read.

## Exercise 6

```{r}
library(rvest)
library(tidyverse)
## provide the URL and name it something (in this case, url).
## paste0 pastes together the base URL and the year into a single string:
## this will be useful in a moment
get_wiki_100 <- function(year) {
  
  ## same code as before, replacing 2017 with year.
  url <- paste0("https://en.wikipedia.org/wiki/Billboard_Year-End_Hot_100_singles_of_", year)
  
  h <- read_html(url)
  
  tab <- h %>% html_nodes("table")
  df <- tab[[1]] %>% html_table() %>%
    mutate(year = year)
  
  ## tell our function to return the dataframe `df`
  return(df) 
}

year_list <- list(2017, 2018, 2019, 2020, 2021)
year_list

df_all <- map(year_list, get_wiki_100)
df_all ## a list of data frames, one for each year

df_2017_present <- bind_rows(df_all) ## combines rows                                        of the 5 new data                                       frames created
df_2017_present <- df_2017_present %>%
  mutate(Title = str_remove_all(Title, pattern = "\"")) %>% ## get rid of \ in title
  rename(no = No., 
         title = Title, 
         artist = `Artist(s)`) ## make column names match with billboard package

wiki_tibble <- as_tibble(wiki_hot_100s) %>% ## convert billboard data to tibble
  mutate(year = as.numeric(year),
         no = as.integer(no)) ## change variable types to match with scraped data

hot100_df <- bind_rows(wiki_tibble, df_2017_present)
```

```{r}
hot100_top15_df <- hot100_df %>% 
  as_tibble() %>% 
  filter(year <= 2019 & year >= 2010) %>%
  group_by(artist) %>%
  summarise(nsongs = n()) %>%
  arrange(desc(nsongs)) %>%
  slice(1:15) %>%
  mutate(artist = fct_reorder(artist, nsongs))
```

```{r}
ggplot(data = hot100_top15_df, aes(x = artist, y = nsongs)) +
  geom_point(size=3, color = "red", shape=18) + 
  coord_flip() + 
  geom_segment(aes(x=artist, xend=artist, y=0, yend=nsongs-0.25), linetype="dotdash", colour="brown")
```

## Exercise 7

The purpose of the "rvest" package is to make the process of scraping data from websites -- like Wikipedia just now -- much easier. We then use the functions in the "purr" package to manipulate the data from the scrape into a usable format. This involves adding vectors, changing titles, etc.


```{r}
install.packages("usethis")
```

## Section 5.2

```{r}
library(tidyverse)
hpi_df <- read_csv("data/hpi-tidy.csv")
```

```{r}
ggplot(data = hpi_df, aes(x = Footprint, y = Wellbeing)) +
  geom_point()
```

```{r}
hpi_us <- hpi_df %>% filter(Country == "United States of America")
hpi_us
```

```{r}
ggplot(data = hpi_df, aes(x = Footprint, y = Wellbeing)) +
  geom_point() +
  geom_label(data = hpi_us, aes(label = Country)) ## specify
```

```{r}
library(ggrepel)
library(plotly)
ggplot(data = hpi_df, aes(x = Footprint, y = Wellbeing)) +
  geom_point() +
  geom_label_repel(data = hpi_us, aes(label = Country)) +
  geom_point(data = hpi_us, size = 3, shape = 1) ## create a second point that is an open circle (shape = 1) with a larger size (size = 3) to surround the United States point on the scatterplot
```


```{r}
plot1 <- ggplot(data = hpi_df, aes(x = Footprint, y = Wellbeing)) +
  geom_point()
```

```{r}
ggplotly(plot1)
plot1 <- ggplot(data = hpi_df, aes(x = Footprint, y = Wellbeing,
                                   label = Country)) +
  geom_point()
ggplotly(plot1, tooltip = "label")
```

```{r}
plot2 <- ggplot(data = wiki_top15, aes(x = artist, y = nsongs, label = artist)) +
  geom_col() + coord_flip()
ggplotly(plot2, tooltip = "label")
```

## Exercise 3

Advantages: interesting, allows user to explore
Disadvantages: requires a computer, adds extra "Stuff", bad for making a particular point about a graph (like Western countries have a high footprint)

## Exercise 4

```{r}
ggplot(data = hpi_df, aes(x = Footprint, y = HappyLifeYears, colour = Region)) +
  geom_point() +
  scale_colour_brewer(palette = "Accent")

ggplot(data = hpi_df, aes(x = Footprint, y = HappyLifeYears, colour = Region)) +
  geom_point() +
  scale_colour_brewer(palette = "Dark 2")

ggplot(data = hpi_df, aes(x = Footprint, y = HappyLifeYears, colour = Region)) +
  geom_point() +
  scale_colour_brewer(palette = "Oranges")
```

## Exercise 5

```{r}
ggplot(data = hpi_df, aes(x = Footprint, y = HappyLifeYears, colour = Region)) +
  geom_point() +
  scale_colour_viridis_d(option = "plasma")

ggplot(data = hpi_df, aes(x = Footprint, y = HappyLifeYears, colour = Region)) +
  geom_point() +
  scale_colour_viridis_d(option = "plasma")
```

## Exercise 6

```{r}
?scale_colour_viridis_d
```

`_d` is for discrete values, `_c` is for continuous variables, and `_b` is for binning continuous variables.

## Faceting

Faceting is more useful if:

*there are "more" categories (tough to differentiate across different colors)
*if there is a lot of overlap in between the groups

```{r}
ggplot(data = hpi_df, aes(x = Footprint, y = HappyLifeYears)) +
  geom_point() +
  facet_wrap( ~ Region)
```

```{r}
library(palmerpenguins)
ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point(aes(colour = species)) ## colour is good enough here
#> Warning: Removed 2 rows containing missing values
#> (geom_point).
```

```{r}
colour_bad <- tibble(x = rnorm(500, 0, 1), y = rnorm(500, 0, 1),
       groupvar = c(rep("A", 50), rep("B", 50),
                    rep("C", 50), rep("D", 50),
                    rep("E", 50), rep("F", 50), rep("G", 50),
                    rep("H", 50), rep("I", 50), rep("J", 50)))

ggplot(data = colour_bad, aes(x = x, y = y, colour = groupvar)) +
  geom_point() + ## can't distinguish anything really: colour is bad
  geom_smooth(se = FALSE)
#> `geom_smooth()` using method = 'loess' and formula 'y ~ x'
```


