---
title: "In-Class Quiz 1"
author: "Jack Sylvia"
date: "1/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

“All work presented is my own. I have not communicated with or worked with anyone else on this quiz.”

Jack Sylvia

1. Group 5 is the easiest to see the overall trend in the count because it is the only group that has a consistent baseline (of 0).
<br>
2.
```{r}
library(tidyverse)
category <- rep(c("Group 1", "Group 2", "Group 3", "Group 4", "Group 5"), 7)
time <- rep(c(2000, 2001, 2002, 2003, 2004, 2005, 2006), each = 5) 
response <- rpois(length(category), 30)
df <- tibble(category, time, response)

ggplot(data = df, aes(x = time, y = response)) +
  geom_col(aes(fill = category)) +
  labs(y = "count") + facet_wrap(~ category)
```
<br>
3a. A diverging color scale should be used because we are looking at percent change as well as the direction of movement in cases.
<br>
3b. We should use a sequential color scale as we are now using only concerned about cases -- the higher the number of the cases the higher the intensity of the color.
<br>
4. Compared to the first visualization at the top of the quiz, the <coordinate_function> parameter was adjuested to have the axes flipped. Also, there was an aesthetic mapping change made to have an axis read "response" instead of "count".
<br>
5a.
```{r}
ggplot(data = df, aes(x = time, y = response), colours("blue")) +
  geom_point(colour = "blue")
```

Since you are not in the ggplot parentheses making an aesthetic mapping with geom_point will not work.
<br>
5b.
```{r}
ggplot(data = df, aes(x = time, y = response)) +
  geom_point() +
  geom_smooth(se = FALSE, span = 1.9)
```

Color was attached to category as aesthetic mapping. Taking that away allowed there to be just a single best fit plot.

