---
title: "In-Class_Quiz_5"
author: "Jack Sylvia"
date: "2/23/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

“All work presented is my own. I have not communicated with or worked with anyone else on this quiz.” - Jack Sylvia

## Question 1

The first graph is appropriate to construct as it shows the amount of samples from each species. The second graph is not appropriate because you cannot discern whether a species has 2 or 2,000,000 penguins -- making the average given less useful to interpret.

## Question 2

```{r}
library(here)
library(tidyverse)
hpi_df <- read_csv(here("data/hpi-tidy.csv"))

hpi_new_df <- hpi_df %>% 
  group_by(Region) %>%
  summarise(
    AvgGDP_person = mean(GDPcapita)
  )

ggplot(data = hpi_new_df, aes(x = Region, y = AvgGDP_person)) +
  geom_point() + 
  coord_flip()
```

## Question 3

```{r}
hpi_Q3_df <- hpi_df %>% 
  group_by(Region) %>%
  summarise(
    GDPcapita_low = min(GDPcapita),
    GDPcapita_high = max(GDPcapita),
    AvgGDP_person = mean(GDPcapita)
  )

ggplot(data = hpi_Q3_df, aes(x = Region, y = AvgGDP_person)) +
  geom_point() + 
  coord_flip() +
  geom_point(aes(y = GDPcapita_low), colour = "red") +
  geom_point(aes(y = GDPcapita_high), colour = "blue") +
  labs(
         red = "GDPcapita_low",
         black = "AvgGDP_person",
         blue = "GDPcapita_high"
        )
```
